---
title: "Group Project"
output: html_notebook
---
```{r}
gproj <- Cost.of.Living.2022
head (gproj, 5)
```
Rent Index with Breaks at 10:


```{r}
hist(gproj$`Rent.Index`, breaks=10, xlab="Rent Index", main="Rent Index")
```
Groceries Index Histogram with breaks at 10:

```{r}
hist(gproj$`Groceries.Index`, breaks=10, xlab="Groceries Index", main="Groceries Index")
```

Groceries Index Histogram with breaks at 5:

```{r}
hist(gproj$`Groceries.Index`, breaks=5, xlab="Groceries Index", main="Groceries Index")
```
Restaurant Price Index Histogram with breaks at 10:

```{r}
hist(gproj$`Restaurant.Price.Index`, breaks=10, xlab="Restaurant Price Index", main="Restaurant Price Index")
```
Restaurant Price Index Histogram with breaks at 5:


```{r}
hist(gproj$`Restaurant.Price.Index`, breaks=5, xlab="Restaurant Price Index", main="Restaurant Price Index")
```

Linear Regression Plot and Correlation of Rent:

```{r}
plot(gproj$`Rent.Index`, gproj$`Cost.of.Living.Index`, xlab="Rent Index", ylab="Cost of Living Index")

myline <- lm(gproj$`Cost.of.Living.Index` ~ gproj$`Rent.Index`)

points(gproj$`Rent.Index`, myline$coefficients[1] + myline$coefficients[2] *
         gproj$`Rent.Index`, type="l", col="red")

```
```{r}
rentx <- gproj$Rent.Index
y <- gproj$Cost.of.Living.Index
cor(rentx,y)
```

Linear Regression Plot and Correlation of Groceries:


```{r}
plot(gproj$`Groceries.Index`, gproj$`Cost.of.Living.Index`, xlab="Groceries Index", ylab="Cost of Living Index")

myline <- lm(gproj$`Cost.of.Living.Index` ~ gproj$`Groceries.Index`)

points(gproj$`Groceries.Index`, myline$coefficients[1] + myline$coefficients[2] *
         gproj$`Groceries.Index`, type="l", col="red")
```
```{r}
grocx <- gproj$Groceries.Index
y <- gproj$Cost.of.Living.Index
cor(grocx,y)
```
Linear Regression Plot and Correlation of Resturant Price:


```{r}
plot(gproj$`Restaurant.Price.Index`, gproj$`Cost.of.Living.Index`, xlab="Restaurant Price Index", ylab="Cost of Living Index")

myline <- lm(gproj$`Cost.of.Living.Index` ~ gproj$`Restaurant.Price.Index`)

points(gproj$`Restaurant.Price.Index`, myline$coefficients[1] + myline$coefficients[2] *
         gproj$`Restaurant.Price.Index`, type="l", col="red")
```
```{r}
restx <- gproj$Restaurant.Price.Index
y <- gproj$Cost.of.Living.Index
cor(restx,y)
```


Summary of data:

```{r}
summary(gproj)
```
View all of the Cost of Living Index values

```{r}
costindex <- gproj$Cost.of.Living.Index
costindex
```

Forming the levels(ranges):

```{r}
cut(costindex,3)
```

```{r}
View(costindex)
```



Assigning Low, Medium and High labels to levels

```{r}
cut(costindex,3, labels = c("Low", "Medium", "High"))
```
Dataset with Range Column added:

```{r}
gproj$Range <- cut(costindex,3, labels = c("Low", "Medium", "High"))
gproj
```

```{r}
View(gproj)
```

Kmeans Clustering

```{r}
gprojK <- subset(gproj, select=c(Rent.Index, Groceries.Index, Restaurant.Price.Index))
```

```{r}
km <- kmeans(gprojK, centers=3)
```

```{r}
gprojM <- data.frame(gproj, km$cluster)
```

```{r}
View(gprojM)
```

Cluster Means for Rent, Groceries and Restaurant Price Only:

```{r}
km
```
```{r}
library(factoextra)
library(cluster)
```


Cluster Plot:

```{r}
fviz_cluster(km, data = gprojK)
```

Each column Mean of each cluster:

```{r}
aggregate(gprojM, by=list(cluster=km$cluster), mean)
```

